### 2010-06-22 trunk/paper/IIWAS2010/content/introduction.tex
Changes after todays review

In addition, Morpheus assumes term categories are come from a \textit{consistent} realm-based ontology. By consistency, we mean it has a clean taxonomy of classes in the ontology class heterachy. This is important because, our proposed similarity measure for categories is based on the heterarchical structure of category ontology. Moreover, when a regular user enters a query, Morpheus ranks SSQs in the store based on this catgeory similarity. Suppose a regular user asks -\textit{ a 1997 Toyota Camry V6 needs what size tires?}. In this query, identifying \textit{Camry V6} as a subclass of \textit{Toyota} cars and a predecessor of \textit{automobile models} is important, because this will help us grouping stored queries. Similarly, a clean ontology-taxonomy can improve the recall of such queries by supporting transitivity and other types of inference like faceted browsing \cite{Wu2008}.

This paper starts with discussing state-of-the-art systems in the area of question answering, ontology generation, and query ranking. The section system architecture explains the Morpheus system and its implementations details. In the results section, we describe current results and its interpretations. Finally, we conclude the paper by describing the global impacts of our approaches in QA systems, WWW page categorization, and ontology generators.

>>>>

In addition, Morpheus assumes term categories are come from a
\textit{consistent} realm-based ontology. By consistency we mean it has two
properties: (i) singly-rooted heterarchy (acyclic digraph wiyh unique 
ancestor of all nodes) (ii) the subclass/superclass relations have meaningful 
semantic interpretations. This is important because, our proposed similarity 
measure for categories is based on the heterarchically
structured category ontologies. Moreover, when a regular user enters a query,
Morpheus ranks SSQs in the store based on this catgeory similarity. Suppose a
regular user asks -\textit{ a 1997 Toyota Camry V6 needs what size tires?}. In
this query, identifying \textit{Camry V6} as a subclass of \textit{Toyota} cars
and a predecessor of \textit{automobile models} is important, because this will
help us grouping stored queries. Similarly, a clean ontology-taxonomy can
improve the recall of such queries by supporting transitivity and other types of
inference like faceted browsing \cite{Wu2008}.

[Need a paragraph for wiki page categorization and ontology construction]
In this paper, we propose an automatic web page categorization or 
classification and recommendation using a machine learning technique, topic modeling.
In addition, we also describes how we can use the categorized pages for realm-ontology 
creation.

This paper starts by discussing state-of-the-art systems in the area of
question answering, ontology generation, and query ranking. The system
architecture section explains the Morpheus system and its implementations
details. In the results section, we describe current results and its
interpretations. Finally, we conclude the paper by describing the global impacts
of our approaches in QA systems, WWW page categorization, and ontology
generators.

### 2010-06-22 trunk/paper/IIWAS2010/content/related_work.tex
Changes after todays review

The extraction procedure is as follows: Wikipedia categories are represented
using skos:concepts and category relations are represented using skos:broader
\cite{Auer07dbpedia:a, Bizer2009}. In fact, DBpedia does not define any new
relation between the Wikipedia categories. The Wikipedia categories are
extracted directly from Wikipedia pages and there is no quality check on the
resultant ontology. Similarly, DBpedia uses the info-box attributes and values
as the ontological relations and its ranges.

YAGO is a partly automatically constructed ontology from Wikipedia and
WordNet\cite{Suchanek2009phd}. The YAGO ontology uses an automated process to
extract information from Wikipedia pages, info-boxes, and categories and to
combine this information with the WordNet\footnote{http://wordnet.princeton.edu} synsets heterarchy. Since Wikipedia contains more individuals in the form of Wikipedia pages than in the man-made WordNet ontology, the Wikipedia page titles are used as the YAGO ontology individuals. YAGO concentrates mainly on the fields of people, cities, events, and movies\cite{Suchanek2009phd}.

@@

Moreover, YAGO type extraction is mainly based on the assumption that
each Wikipedia page has at least one tagged category, and the assigned Wikipedia
categories are relevant to that Wikipedia page. The Wikipedia page category assignments are subjectively assigned by human editors and some Wiki pages could be left unassigned i.e., they have no category unintentionally. In addition, we cannot completely rely on the relevance of these assigned Wikipedia page categories. To overcome these issues, we propose an automatic Wikipedia page categorization or classification and recommendation using a machine learning technique, topic modeling.

>>>>

The extraction procedure is as follows: Wikipedia categories are represented
using skos:concepts and category relations are represented using skos:broader
\cite{Auer07dbpedia:a, Bizer2009}. In fact, DBpedia does not define any new
relations between the Wikipedia categories. The Wikipedia categories are
extracted directly from Wikipedia pages and there is no quality check on the
resultant ontology. Similarly, DBpedia uses the info-box attributes and values
as the ontological relations and its ranges.

YAGO is a semi-automatically constructed ontology from Wikipedia and
WordNet\cite{Suchanek2009phd}. The YAGO ontology uses an automated process to
extract information from Wikipedia pages, info-boxes, and categories and to
combine this information with the WordNet\footnote{http://wordnet.princeton.edu}
synsets heterarchy. Since Wikipedia contains more individuals in the form of
Wikipedia pages than in the man-made WordNet ontology, the Wikipedia page titles
are used as the YAGO ontology individuals. YAGO concentrates mainly on the
fields of people, cities, events, and movies\cite{Suchanek2009phd}.

@@

Moreover, YAGO type extraction is mainly based on the assumption that
each Wikipedia page has at least one tagged category, and the assigned Wikipedia
categories are relevant to that Wikipedia page. The Wikipedia page category
assignments are subjectively assigned by human editors and some Wiki pages are
unassigned i.e., they have no category. In addition, we cannot completely rely
on the relevance of these assigned Wikipedia page categories.
